Matching Bullets

### 2015-12-09 imaging-paper.Rnw
Linetype for circle fits

\begin{figure}[hbtp]
  \centering
<<circlefits, echo=FALSE, fig.width=7, fig.height=7, out.width='\\linewidth', warning=FALSE>>=
qplot(y, resid, data=subset(db2, x == 100), #colour=factor(x), 
      geom="line", size=I(.75), colour=I("grey70")) + 
  facet_wrap(~part, ncol=2) + scale_colour_brewer(palette="Paired") +
  theme_bw() + theme(legend.position="bottom") + 
  geom_line(aes(y, resid, group = x), colour="black", size=.75, alpha=0.5,
             data = filter(db1, part==5, x == 100)[,c("y", "resid", "x")]) +
  ylab("Residuals from circular fit") +
  ggtitle("Land 5 of Bullet 1 in black")
@
\caption{Circle fit for each cross section of bullet 2, with land 5 of bullet 1 overlaid.\label{fig:circlefits} \hh{Land 5 of bullet 1 matches best with the first land of the second bullet.}}%
\end{figure}

>>>>

\begin{figure}[hbtp]
  \centering
<<circlefits, echo=FALSE, fig.width=7, fig.height=7, out.width='\\linewidth', warning=FALSE>>=
qplot(y, resid, data=subset(db2, x == 100), #colour=factor(x), 
      geom="line", size=I(.75), linetype=I(3)) + 
  facet_wrap(~part, ncol=2) + scale_colour_brewer(palette="Paired") +
  theme_bw() + theme(legend.position="bottom") + 
  geom_line(aes(y, resid, group = x), linetype=1, size=.75,
             data = filter(db1, part==5, x == 100)[,c("y", "resid", "x")]) +
  ylab("Residuals from circular fit") +
  ggtitle("Land 5 of Bullet 1 in black")
@
\caption{Circle fit for each cross section of bullet 2, with land 5 of bullet 1 overlaid.\label{fig:circlefits} \hh{Land 5 of bullet 1 matches best with the first land of the second bullet.}}%
\end{figure}
